Evaluating procedures for updating catch advice between stock assessments of reef fishes with management strategy evaluation

### 2022-03-30 RunMSE/SEFSC/MSEPlots.Rmd
recent runs

scenNames_user1 <-  c("base","dep","lf","ucvhi","ubias","ucvlo")
scenNames_user2 <-  c("base","rc","minerr","minrecdev","vtiv")
scenNames_user3 <-  c("base","noempind",
                      "nolag","perfobs","tachi")
scenNames_user4 <-  c("base","lhset","Mset","steepset","agevarM"#,"epiM"
                      )

# All scenarios
scenNames_user <- unique(c(scenNames_user1,scenNames_user2,scenNames_user3,scenNames_user4))

@@

scenNames_key <- c("agevarM"="Age-varying M",
                   "base"="Base",
                   "dep"="Depleted",
                   "epiM"="Episodic M",
                   "hd"="Hyper-deplete",
                   "hs"="Hyper-stable",
                   "lf"="Lightly fished",
                   "lhset"="Set M and steep",
                   "mconst"="M constant",
                   "minerr"="Minimal error",
                   "minrecac"="Minimal rec AC",
                   "minrecdev"="Minimal rec devs",
                   "Mset"="Set M",
                   "noempind"="No empirical indices",
                   "nolag"="No data lag",
                   "perfobs"="Perfect observation",
                   "rc"="Regime\nchange",
                   "steepset"="Set steepness",
                   "tachi"="TAC 1.25MSY",
                   "ubias"="Index\nbiased",
                   "ucvhi"="Index\nHigh CV",
                   "ucvlo"="Index\nLow CV",
                   "vtiv"="V time invariant"
                   )

@@

```{r plot time series4,eval=TRUE}
# # VB
# plot_MSE_ts(
# OMNames= OMNames, scenNames=scenNames_user4,
# myvarName = "VB",
# ylabel = expression(mean~(VB)),
# FUN = mean,
# MPNamesSub = MPNamesSub_user,
# MPNamesSub_legtext=MPNamesSub_user_legtext,
# rowLabs=scenNames_key[scenNames_user4]
# )

@@

if(plot_pdf){pdf("Figs/phasePlot4.pdf")}
plot_MSE_ts(
  OMNames= OMNames, scenNames=scenNames_user4,
  plot_type = "phase",
  proyear_phase=41:50,
  MPNamesSub = c(MPNamesSub_user),
  MPNamesSub_legtext=c(MPNamesSub_user_legtext),
  rowLabs=scenNames_key[scenNames_user4],
  mar=c(0,0,0,0),label_axes="leftbottom",
  xlim=c(0,5),ylim=c(0,5),
  hline=NA
)
if(plot_pdf){dev.off()}
```

>>>>

scenNames_user1 <-  c("base","dep","lf","ucvhi","ubias","ucvlo")
scenNames_user2 <-  c("base","rc","minerr","minrecdev","recns","vtiv")
scenNames_user3 <-  c("base","noempind","catcvlo","nolag","perfobs","tachi")
scenNames_user4 <-  c("base","lhset","Mset","steepset","agevarM","epiM")

# All scenarios
scenNames_user <- unique(c(scenNames_user1
                           ,scenNames_user2
                           ,scenNames_user3
                           #,scenNames_user4
                           ))

@@

scenNames_key <- c("agevarM"="Age-varying M",
                   "base"="Base",
                   "catcvlo"="Catch CV 0.05",
                   "dep"="Depleted",
                   "epiM"="Episodic M",
                   "hd"="Hyper-deplete",
                   "hs"="Hyper-stable",
                   "lf"="Lightly fished",
                   "lhset"="Set M and steep",
                   "mconst"="M constant",
                   "minerr"="Minimal error",
                   "minrecac"="Minimal rec AC",
                   "minrecdev"="Minimal rec devs",
                   "Mset"="Set M",
                   "noempind"="No empirical indices",
                   "nolag"="No data lag",
                   "perfobs"="Perfect observation",
                   "rc"="Regime\nchange",
                   "recns"="Recruitment\nnonstationary",
                   "steepset"="Set steepness",
                   "tachi"="TAC 1.25MSY",
                   "ubias"="Index\nbiased",
                   "ucvhi"="Index\nHigh CV",
                   "ucvlo"="Index\nLow CV",
                   "vtiv"="V time invariant"
                   )

@@

```{r plot time series4,eval=FALSE}
# # VB
# plot_MSE_ts(
# OMNames= OMNames, scenNames=scenNames_user4,
# myvarName = "VB",
# ylabel = expression(mean~(VB)),
# FUN = mean,
# MPNamesSub = MPNamesSub_user,
# MPNamesSub_legtext=MPNamesSub_user_legtext,
# rowLabs=scenNames_key[scenNames_user4]
# )

@@

# if(plot_pdf){pdf("Figs/phasePlot4.pdf")}
# plot_MSE_ts(
#   OMNames= OMNames, scenNames=scenNames_user4,
#   plot_type = "phase",
#   proyear_phase=41:50,
#   MPNamesSub = c(MPNamesSub_user),
#   MPNamesSub_legtext=c(MPNamesSub_user_legtext),
#   rowLabs=scenNames_key[scenNames_user4],
#   mar=c(0,0,0,0),label_axes="leftbottom",
#   xlim=c(0,5),ylim=c(0,5),
#   hline=NA
# )
# if(plot_pdf){dev.off()}
```

### 2022-03-30 RunMSE/SEFSC/Manuscript/MainText.Rnw
recent runs

Response variables tended to vary among time periods over the projection years, and therefore plotted by time period.
In general, stock status ($SSB/SSB_{MSY}$) was similar among all nine SCA-based MPs for all four species, pooling across scenarios (Fig. \ref{fig:boxplotSBSBMSY1}). However MPs that adjusted between assessments with a buffered index approach tended to show slightly higher stock status for Black Sea Bass and Vermilion Snapper. Fishery status ($F/F_{MSY}$) was somewhat more variable, but still largely consistent among SCA-based MPs, for all species. For Black Sea Bass and Vermilion Snapper, $F/F_{MSY}$ for buffered index MPs tended to be at the low end of the range of the other MPs. Similarly, total catch was also similar among SCA-based MPs for all species, for similar time periods. Average annual variability in yield (catch) showed more substantial variation among MPs.

@@

% Indices
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in,height=7in]{../Figs/AddInd.pdf}
\end{center}
\begin{flushleft}
\caption{Indices derived from BAM stock assessments available during the projection period, for the SCA\_5 MP in the Base scenario. Shaded areas represent 95\% CI for indices among simulation runs.}
\label{fig:AddInd}
\end{flushleft}
\end{figure}

>>>>

Response variables tended to vary among time periods over the projection years, and are therefore plotted by time period. In general, stock status ($SSB/SSB_{MSY}$) was similar among all nine SCA-based MPs for all four species, pooling across scenarios (Fig. \ref{fig:boxplotSBSBMSY1}). However MPs that adjusted between assessments with a buffered index approach tended to show slightly higher stock status for Black Sea Bass and Vermilion Snapper. Fishery status ($F/F_{MSY}$) was somewhat more variable, but still largely consistent among SCA-based MPs, for all species. For Black Sea Bass and Vermilion Snapper, $F/F_{MSY}$ for buffered index MPs tended to be at the low end of the range of the other MPs. Similarly, total catch was also similar among SCA-based MPs for all species, for similar time periods. Average annual variability in yield (catch) showed more substantial variation among MPs.

@@

% Indices
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in,height=7in]{../Figs/AddInd.pdf}
\end{center}
\begin{flushleft}
\caption{Indices derived from BAM stock assessments available during the projection period, for the SCA\_10 MP in the Base scenario, where stock assessments are conducted every 10 years during the projection period (dashed vertical lines). Shaded areas represent 95\% CI for indices among simulation runs.}
\label{fig:AddInd}
\end{flushleft}
\end{figure}
